Classless Java

### 2015-09-09 paper/paper.tex
overview: Point example

@@

@@

Collections example from traits paper?

>>>>

We provide a Java annotation \mixin to provide default implementations for
various methods and a mechanism to instantiate objects. \mixin annotation helps
programmers to write less cumbersome code and instantiate interfaces in Java.

For example, interface \texttt{Point} annotated with \mixin:

@@

\texttt{Point} has two (conceptually) member fields \texttt{X} and
\texttt{Y}. Methods \texttt{int X()} and \texttt{int Y()} serve as \emph{getter}
methods. Methods \texttt{void X(int X)} and \texttt{void Y(int Y)} serve as
\emph{setter} methods. Method \texttt{Point withX(int X)} updates field
\texttt{X} and returns \textbf{this}.

A typical and trivial implementation that programmers usually do is:

\lstinputlisting[linerange=79-109]{../UseMixinLombok/src/test/TestLombok.java} % APPLY:linerange=POINTIMPL

@@

Collections example from traits paper? 
(\yanlin{couldn't found source code})
